Evaluating computational methods for modeling off-normal operation of gas centrifuge cascades

### 2018-06-27 paper.tex
Add title
intagrating some gonuke comments

\documentclass{anstrans}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\title{}
\author{Baptiste Mouginot, Kathryn Mummah, Paul P.H.  Wilson}

\institute{
University of Wisconsin-Madison, Madison, WI
}

\email{mouginot@wisc.edu \and mummah@wisc.edu \and paul.wilson@wisc.edu}

% Optional disclaimer: remove this command to hide
% \disclaimer{Notice: this manuscript is a work of fiction.  Any resemblance to
% actual articles, living or dead, is purely coincidental.}

%%%% packages and definitions (optional)
\usepackage{graphicx} % allows inclusion of graphics
\usepackage{booktabs} % nice rules (thick lines) for tables
\usepackage{microtype} % improves typography for PDF
\usepackage{float}

\newcommand{\SN}{S$_N$}
\renewcommand{\vec}[1]{\bm{#1}} %vector is bold italic
\newcommand{\vd}{\bm{\cdot}} % slightly bold vector dot
\newcommand{\grad}{\vec{\nabla}} % gradient
\newcommand{\ud}{\mathop{}\!\mathrm{d}} % upright derivative symbol
\newcommand{\ie}{\emph{i.e.\ }}

\usepackage[acronym]{glossaries}
\newacronym{UOX}{UOX}{uranium oxide fuel}
\newacronym{MOX}{MOX}{mixed oxide fuel}
\newacronym{LWR}{LWR}{light water reactor}
\newacronym{SFR}{SFR}{fast breeder reactor}

\begin{document}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}

Fuel cycle simulations, as with any simulation process, do not produce results
without uncertainties.  Those uncertainties have two main sources: modeling
uncertainty due to the simplifications and approximations built in to the
simulator itself, and data uncertainty from the quantities provided by the
user. This work focuses on a subset the data uncertainty related to
the user input that defines the performance of the simulated facilities.

Such simulation uncertainties could be important in the context of treaty
verification.  Some scenarios require estimating historical fissile material
production based on records of facility operation and material transfer.  If
the measurements of facility operation and material transfer are subject to
uncertainty, the total production quantities will then also be uncertain.  Any
uncertainty in fissile production quantities poses a material accounting
challenge, possibly creating an opportunity for undetected diversion.

This study seeks to understand which characteristics of facility operation have the
most impact on the uncertainty of fissile material production across a complete
fuel cycle.  Uncertainty propagation using a Monte Carlo method will be applied
to the Cyclus fuel cycle simulator \cite{cyclus} to estimate the effect of
individual facility uncertainties on the output metrics. The same simulation
will be performed $N$ times, with some input parameters randomly determined in each case.
The distribution of each output metrics over the N trials of the simulation
will be used to estimate their
respective uncertainty.

\section{The Experiment}

\subsection{Method}

To estimate the uncertainty of fuel cycle output metrics, a Monte
Carlo approach has been applied.  In each of 199 independent simulations,
some of the parameters that define facility behavior are randomly selected
from Normal distributions with standard deviations that are $10\%$ of the mean/nominal
value.  This artificially large standard deviation is selected for the purpose
of demonstrating the methodology.  The mean and standard deviation of some
output metrics are calculated from the simulation output, as a function of time.

To pursue this work, both the Cycamore\footnote{Low
fidelity facilities package for Cyclus}\cite{cycamore} and the
CyCLASS\footnote{Reactor and fuel fabrication facility based on CLASS\cite{CLASS} models}\cite{mouginot_2018, cyclass} packages were
updated to evaluate the uncertainty of several
operational parameters in their associated facilities.  Table
\ref{tab:package_uncertainty} summarizes all uncertainty-tracking modifications implemented in the
facilities of Cycamore and CyCLASS.

\begin{table}[htb]
\centering
  \caption{Summary of facility modifications according to their Cyclus archetype package.}
\begin{tabular}{cl|l}
\toprule

Package   & Facility   & Parameters                \\
\toprule

Cycamore & Separation & Separation efficiency     \\\cmidrule{2-3} 
         & Storage    & Residence Time            \\
\toprule
CyCLASS  & Reactor    & Cycle Length              \\\cmidrule{3-3}
         &            & Power                     \\\cmidrule{3-3}
         &            & \acrshort{LWR}-\acrshort{UOX} Fuel Enrichment\\

\bottomrule
\end{tabular}

  \label{tab:package_uncertainty}
\end{table}

The uncertainty of the different parameters in this study
are systematic for each new deployed facility: each time a new facility is
deployed (such as a reactor or a fuel fabrication facility) a new set of
parameters are sampled, and those parameters are used throughout the life
of that facility.

\subsection{The Fuel Cycle Scenario}
For demonstration purposes, a simple commercial fuel cycle transition is used,
inspired from the EG23 fuel cycle
of the Nuclear Fuel Cycle Evaluation and Screening Report\cite{ES}.
Pictured in Figure \ref{fig:cycle}, this is a
transition from a \gls{LWR} fleet loaded with \gls{UOX} fuel to a
\gls{SFR} fleet loaded \gls{MOX} fuel, considering a $1\%/$y growth
of the nuclear generated power (Figure \ref{fig:power}).
\begin{figure}[b] % replace 't' with 'b' to force it to be on the bottom
  \centering
  \includegraphics[scale=0.31]{cycle.png}
  \caption{Simplified representation of the material flow between the different facilities,
  with each operational parameter associated with an
  uncertainty labeled in green.}\label{fig:cycle}
\end{figure}

As illustrated in Figure \ref{fig:power}, the transition starts with a fleet
composed of only \glspl{LWR} loaded with enriched \gls{UOX} fuel.  The actual
transition starts around year 35, with the deployment of \glspl{SFR}. The \glspl{SFR} are loaded
with \gls{MOX}, which consists of plutonium blended with natural
uranium.

\begin{figure}[t] % replace 't' with 'b' to force it to be on the bottom
    \centering
    \includegraphics[scale=0.18]{power.png}
    \caption{Electric power generated over time, including contributions from each reactor type.}
    \label{fig:power}
\end{figure}

The plutonium, required for \gls{MOX} fabrication, is reprocessed from all
used fuel.  At first, it is sourced only from \gls{UOX}, then used \gls{MOX} fuel
as it becomes available for reprocessing.

Both fuel reprocessing and fabrication have a constant maximum throughput, but may also be limited by the 
availability input material.  The enrichment of the \gls{UOX} is processed
on demand.  Buffer storage facilities (not shown in Figure \ref{fig:cycle}) are present
between all facilities with constant throughput.

In this work, a time step of 1 month has been considered, \ie each output
metric is reported once per month. Additionally, decay processes have not be
taken into account.

It must be noted that for this work, the fuel enrichment was determined by a
fuel fabrication model\cite{Leniau2015125} which
calculates the fissile fraction required in the fuel to reach a given target
burnup at the end of irradiation.  Therefore, the uncertainty of the fuel
enrichment is not applied directly to the effective enrichment. It is instead applied to the
burnup, resulting in a fuel enrichment uncertainty that is also close to
$10\%$.

For each of the parameters in Table \ref{tab:package_uncertainty}, a set of
199 simulations was performed with only that parameter being randomly varied.
An additional set of 199 simulations was performed in which all five
parameters are randomly varied.  A reference simulation was performed
with all five parameters fixed at the mean value.

\section{Results}

Because the main interests of nuclear archaeology involve highly enriched uranium production and
fissile inventories, this study mainly focuses on the uncertainties of
the total quantity of natural uranium used and the total unused fissile
inventory (separated plutonium).

The total power generated in the simulation is reviewed to ensure that none of
the compounded uncertainties result in material shortages substantial enough to
cause long term facility shutdowns.  For example, since \gls{SFR} fuel is built
from reprocessed used fuel, availability of that used fuel may impact the
capability to build the required \gls{SFR}-\gls{MOX} fuel.  While there may be studies in
which this would be an interesting result, in the context of this work, such
shutdowns would be well-documented in the operational histories of the
facilities and should not be characterized as an uncertainty.  Figure
\ref{fig:power_full} shows that uncertainties in generated power are indeed
very low.

\begin{figure}[t] % replace 't' with 'b' to force it to be on the bottom
    \centering
    \includegraphics[scale=0.3]{power_full}
    \caption{Electric power generated as a function of time, wit its uncertainty.}\label{fig:power_full}
\end{figure}

At each time step, the $\pm1\sigma$ uncertainty due to the full set of varied
parameters is reported.  In addition, the relative contribution to the total
uncertainty from each of the parameters is calculated as the ratio of the
$1\sigma$ uncertainty due to that parameter over the total uncertainty.

\subsection{Natural Uranium Consumption Dedicated to \gls{LWR}-\gls{UOX} fabrication}

Figure \ref{fig:unat_full} represents the cumulative natural uranium consumption
dedicated to \gls{LWR}-\gls{UOX} fuel fabrication as a function of time.  The uncertainty on
the cumulative uranium consumption grows as expected with the time and the
loading of the \glspl{LWR}.  The increase stops around year 125y with the
decommissioning of the last \glspl{LWR}.

As expected, cooling time, separation efficiency and thermal power do not
affect the natural uranium consumption for \gls{LWR}-\gls{UOX} fuel production.  The uncertainty on the natural uranium
consumption is dominated by the \gls{LWR} cycle length: shorter the cycle
length is, the more fuel will be loaded, and \emph{vice versa}.

\begin{figure}[t] % replace 't' with 'b' to force it to be on the bottom
    \centering
    \includegraphics[scale=0.3]{unat_full}
    \caption{Cumulative consumption of natural uranium as a function of time, with
      associated uncertainty.}\label{fig:unat_full}
\end{figure}

\begin{figure}[t] % replace 't' with 'b' to force it to be on the bottom
    \centering
    \includegraphics[scale=0.3]{unat_uncer}
    \caption{Relative uncertainty of the cumulative natural uranium consumption, including
      individual contributions from each varied parameter.}\label{fig:unatr_uncer}
\end{figure}
The relative uncertainty of the total uranium consumption starts at about
$5.5\%$ a slowly drops and stabilize around $3\%$.

Uncertainty fluctuation of the full relative uncertainty can be observed before
year 50.  Those fluctuation are induced by the fuel loading: all reactors at the
beginning of the simulation have synchronized fuel cycles, reloading in the same time step.
This phenomenon disappears
with the gradual decommissioning of the initial reactors, spread over 50 years.

The decrease of the cycle time uncertainty contribution, from year 30 to year
90, can be understood as an averaging effect.  As the uncertainty are defined once
per deployed facility, each reactor will have a different cycle
length value, so a different number of batches loaded per year.  With the increase
of deployed reactors, the number of batches of \gls{LWR} fuel loaded converges
to the references one, reducing its impact on the uncertainty on the total
uranium consumption. This uncertainty contribution to the overall uncertainty
decrease is proportional to the number of \gls{LWR} reactors and stops with the
decommission of the last one.

The fuel enrichment contribution follow a close to constant uncertainty
contribution of $2\%$, so as the total relative uncertainty decrease, it
has a growing shared of the total absolute uncertainty over time.

\subsection{Fissile Inventory}
The fissile inventory corresponds to the amount of separated fissile material waiting to
be blended with natural uranium in order to produce the \gls{SFR}-\gls{MOX} fuel.

As observed on Figure \ref{fig:pu_full}, the fissile inventory starts to grow in
year 40, with the deployment of the first reprocessing facility.  It grows
during the first period of the \glspl{LWR} to \gls{SFR}-A transition until
year 90, then decrease slightly as the last \glspl{LWR} are decommissioned.
When the steady state is reached (full \gls{SFR} fleet), the plutonium
inventory starts to increase, as the breading ratio of the \glspl{SFR} is higher
than the deployment needs.

\begin{figure}[t] % replace 't' with 'b' to force it to be on the bottom
    \centering
    \includegraphics[scale=0.3]{pu_full}
    \caption{Fissile (plutonium) inventory as a function of time, with
      associated uncertainty.}\label{fig:pu_full}
\end{figure}

\begin{figure}[t] % replace 't' with 'b' to force it to be on the bottom
    \centering
    \includegraphics[scale=0.3]{pu_uncer}
    \caption{Relative uncertainty in the fissile (plutonium) inventory, with
      individual contributions from each varied parameter.}\label{fig:pu_uncer}
\end{figure}

At the onset of fissile material production, very low mean inventories lead to
unreliable artifacts in the relative uncertainty.
After that, the relative uncertainty
starts at about $5\%$ and grows until year
125, then decreases to $10\%$ at the end of the simulation time (180y).  
Between year 40 and 70, the main contributor to the fissile inventory
uncertainty is the cycle length.  As with the uranium needs, different cycle length
implies different number of fuel loads, so different amount of resources used.  Nevertheless, around year 65 (see Figure
\ref{fig:used_fuel}), the stock of used fuel available for reprocessing becomes
small enough to start limiting the production of fissile material.
The dominant contribution to the uncertainty then slowly transitions from
the cycle length to the fuel cooling time.

\begin{figure}[t] % replace 't' with 'b' to force it to be on the bottom
    \centering
    \includegraphics[scale=0.16]{used_fuel}
    \caption{Used fuel inventory, corresponding to the amount of used
    \glspl{LWR} and \glspl{SFR} fuel, cooled and waiting to be reprocessed.}
    \label{fig:used_fuel}
\end{figure}
Between year 90 and 120, the \gls{SFR} deployment speed increases; it has to
compensate the non-replacement of the decommissioned \glspl{LWR} as well as
follow the growing power demand.  During this period the needs in plutonium are higher
than its production, explaining the observed decrease of the total amount, and
the increase associated relative uncertainty.

As the transition ends, the plutonium bred from the \glspl{SFR} starts to be
sufficient to sustain the new \gls{SFR} deployment to follow the power demand.

It is also interesting to note that, the uncertainty contribution from the cycle
length between year 40 and 70 comes mainly from fuel batch loading
frequencies.  After 70 years this contribution follows the thermal
power contribution closely, suggesting that fuel discharge burnup (\ie fuel
discharge composition) is the mechanism of this contribution.

\subsection{Discussion}

Uranium consumption and separated fissile inventory are two important metrics
related to non-proliferation and nuclear archaeology.  In this study, we have
been able to estimate that the cycle length uncertainty of $10\%$ implies a
variation of $3\%$ to $5\%$ on the total uranium needs uncertainty, whereas about
$10\%$ uncertainty on the enrichment implies an almost constant uncertainty of $2\%$.

Regarding the reprocessed fissile inventory, this study has shown the 
impact of the reprocessed fuel compositions (through burnup variations) is
limited to $\approx5\%$, while fuel availability constraints, such as fuel loading frequency (cycle
time) or fissile materials available for fuel fabrication (cooling time) can lead to higher
uncertainties, up to $10\%$ and to $30\%$, respectively.  Moreover, it is very
interesting to observe the transition from one to the other around
year 70.

This preliminary study may suggest that the most important contributions to
natural uranium consumption and fissile inventory come from the parameters that
govern the exchange of material between facilities, and not
from the physical parameters that describe those facilities, such as thermal power or fuel enrichment. Further
analysis should allow us to understand this further.

\section{Conclusion}

Two main points can be deduced from this work.  First, in a transitional
fuel cycle, uncertainty contributions to output metrics can vary over time
depending of various factors: deployment schedule artifacts or material flow constrictions.

Second, it is important to note the special character of the time related
parameters uncertainty in a fuel cycle study, such as cooling time and cycle
length.  While some of those time related parameters will, to first order, only
impact material availability (as the cooling time will do), others, like
cycle length, will also have a impact as physical parameters such as fuel
enrichment or thermal power.

Cycle length impacts the discharge fuel burnup and  the frequency of
the fuel loads.  When they combine to produce in uncertainty of the
material availability, this could result in variations related to time delays that may
contribute to the final uncertainty in ways that are not relevant to some analyses.
That is, a simple time lag in a particular output that otherwise follows an identical history
could manifest itself as a large variation at any particular time.
Those kind of time related uncertainties will require a further analysis
to understand and measure accurately their
contributions to the total uncertainty.

This study aims to be a proof-of-principle for uncertainty propagation in
potential commercial fuel cycle transition.  While it has demonstrated the
capability to measure the uncertainty on output fuel cycle metrics and their
relative contributions, it has only been applied to systematic uncertainties per
facilities.
This kind of study will to be extended to random uncertainty (new parameter
values as a function of time) and completely systematic uncertainty (shared by all
the facilities of a kind).

While the parameters contributing to natural uranium needs and fissile inventory
uncertainties might be obvious, such study allows to estimate each parameters
contribution, and it could be less obvious for other parameters, such as
plutonium quality, waste compositions.  Such studies could also provide research
guidance for nuclear archaeology work, which aims to precisely estimate past
fissile production by the different nuclear countries.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Acknowledgments}
This work was funded by the Consortium for Verification Technology under
Department of Energy National Nuclear Security Administration award number
DE-NA0002534

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\bibliographystyle{ans}
\bibliography{bibliography}
\end{document}

>>>>

\documentclass[12pt]{article}
\usepackage{mathptmx} % Nearly Times New Roman
\usepackage[affil-it]{authblk}

%\makeglossaries
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\usepackage{color}
\usepackage{subcaption}
\usepackage{graphicx}
\usepackage{booktabs} % nice rules for tables
\usepackage{microtype} % if using PDF
\usepackage{xspace}
\usepackage{listings}
\usepackage{textcomp}
\usepackage{multicol,tabularx,capt-of}
\usepackage{multirow}

\usepackage{fancyhdr} % allows headers and footers
%\usepackage{ulem}
\usepackage{pdflscape}
% Page length commands go here in the preamble
\setlength{\oddsidemargin}{-0.25in} % Left margin of 1 in + 0 in = 1 in
\setlength{\textwidth}{7in}   % Right margin of 8.5 in - 1 in - 6.5 in = 1 in
\setlength{\topmargin}{-.75in}  % Top margin of 2 in -0.75 in = 1 in
\setlength{\textheight}{9.2in}  % Lower margin of 11 in - 9 in - 1 in = 1 in

\definecolor{listinggray}{gray}{0.9}
\definecolor{lbcolor}{rgb}{0.9,0.9,0.9}
\definecolor{burgundy}{rgb}{0.5, 0.0, 0.13}
\definecolor{burntorange}{rgb}{0.8, 0.33, 0.0}
\definecolor{chromeyellow}{rgb}{1.0, 0.65, 0.0}
\definecolor{darkred}{rgb}{0.55, 0.0, 0.0}

\lstset{
    %backgroundcolor=\color{lbcolor},
    language={C++},
    tabsize=4,
    rulecolor=\color{black},
    upquote=true,
    aboveskip={1.5\baselineskip},
    belowskip={1.5\baselineskip},
    columns=fixed,
    extendedchars=true,
    breaklines=true,
    prebreak=\raisebox{0ex}[0ex][0ex]{\ensuremath{\hookleftarrow}},
    frame=single,
    showtabs=false,
    showspaces=false,
    showstringspaces=false,
    basicstyle=\scriptsize\ttfamily\color{green!40!black},
    keywordstyle=\color[rgb]{0,0,1.0},
    commentstyle=\color[rgb]{0.133,0.545,0.133},
    stringstyle=\color[rgb]{0.627,0.126,0.941},
    numberstyle=\color[rgb]{0,1,0},
    identifierstyle=\color{black},
    captionpos=t,
}

\newcommand{\code}[1]{\lstinline[basicstyle=\ttfamily\color{green!40!black}]|#1|}
\newcommand{\units}[1] {\:\text{#1}}%
\newcommand{\SN}{S$_N$}
\newcommand{\cyclus}{\textsc{Cyclus}\xspace}
\newcommand{\Cyclus}{\cyclus}
\newcommand{\citeme}{\textcolor{red}{CITE}\xspace}
\newcommand{\TODO}[1] {{\color{red}\textbf{TODO: #1}}}%

\newcommand{\comment}[1]{{\color{green}\textbf{#1}}}

\usepackage[acronym]{glossaries}

\input{glossary}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\begin{frontmatter}
\title{Evaluating computational methods for modeling off-normal operation of gas centrifuge cascades}
% Authors. Separated by commas
\input{authors}
\date{}
% Institutes of the authors
\input{institutions}
\pagestyle{fancy}
\begin{document}

\maketitle

% 0.Abstract
\input{abstract}
% I.   Motivation
\input{motivation}

% II.  Theory
%   a. cascade design
%   b. misuse model
%       i.   case A
%       ii.  case B
%       iii. case C
\input{theory}

% III. Experiement
%   a.  cycle 
%   b.  cascade per level optimisation
\input{experiement}

% IV.  results
%   a. time step effects
%   b. no tails recycling
%   c. tails recycling
\input{results}

% V.  Discussion
% VI. Conclusions and future plan
\input{dis_clusion}

\section{Acknowledgments}
This work was funded by the Consortium for Verification Technology under
Department of Energy National Nuclear Security Administration award number
DE-NA0002534

%\end{frontmatter}

%\input{appendix}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{small}
\bibliographystyle{ans}
\bibliography{refs}  % NO SPACES BETWEEN BIB FILENAMES!
\end{small}
\end{document}

### 2018-06-27 results.tex
intagrating some gonuke comments

Model       &        &           & A/NR      & A/R       & B/NR      & B/R      & C/NR       & C/R          \\
%Recycling   &        &           & No        & yes       & No        & Yes     & No        & yes        \\
\midrule                                                                                                 
        &            & Feed      & $0.71w\%$ & $1.3w\%$  & $0.71w\%$ & $0.94w\%$ & $0.71w\%$ & $1.66w\%$ \\
Level 0 & Assay      & Product   & $4.13w\%$ & $7.7w\%$  & $4.13w\%$ & $5.43w\%$ & $4.13w\%$ & $9.53w\%$ \\
        &            & Tail      & $0.29w\%$ & $0.5w\%$  & $0.29w\%$ & $0.39w\%$ & $0.29w\%$ & $0.69w\%$  \\
        & Cascades   &           & 26.73     & 26.45     & 26.6      & 25.8      & 26.73     & 26.45      \\
\midrule                                                                                                 
        &            & Feed      & $4.13w\%$ & $11.9w\%$ & $4.13w\%$ & $6.84w\%$ & $4.13w\%$ & $13.0w\%$ \\
Level 1 & Assay      & Product   & $22.8w\%$ & $55.7w\%$ & $20.6w\%$ & $30.7w\%$ & $22.9w\%$ & $69.8w\%$ \\
        &            & Tail      & $1.8w\%$  & $6.6w\%$  & $1.72w\%$ & $2.91w\%$ & $1.81w\%$ & $9.43w\%$  \\
        & Cascades   &           & 2.92       & 3.20      & 2.91      & 3.41     & 2.92      & 3.20       \\
\midrule                                                                                                 
        &            & Feed      & $22.8w\%$ & $55.7w\%$ & $20.6w\%$ & $34.3w\%$ & $22.9w\%$ & $72.6w\%$ \\
Level 2 & Assay      & Product   & $78.5w\%$ & $95.0w\%$ & $61.0w\%$ & $75.8w\%$ & $82.0w\%$ & $98.4w\%$ \\
        &            & Tail      & $4.12w\%$ & $50.9w\%$ & $9.56w\%$ & $17.5w\%$ & $15.7w\%$ & $69.4w\%$ \\
        & Cascades   &           & 0.31      & 0.35      & 0.37      & 0.64      & 0.32      & 0.35      \\
\midrule                                                                                                 
        &            & Feed      & $78.5w\%$ & N.A.      & $61.0w\%$ & $75.8w\%$ & $82.3w\%$ & N.A.      \\
Level 3 & Assay      & Product   & $98.2w\%$ & N.A.      & $90.4w\%$ & $95.0w\%$ & $99.1w\%$ & N.A.      \\
        &            & Tail      & $76.1w\%$ & N.A.      & $79.3w\%$ & $56.1w\%$ & $80.3w\%$ & N.A.      \\
        & Cascades   &           & 0.03      & N.A.      & 0.080     & 0.18      & 0.03      & N.A.      \\
\bottomrule
\end{tabular}
  \label{tab:level}
\end{table}

@@

\begin{figure}[h!]
    \centering
    \begin{subfigure}[t]{0.45\textwidth}
        \centering
        \includegraphics[scale=0.17]{NR_case1}
        \caption{No tail recycling}
        \label{sfig:case1_NR}
    \end{subfigure}%
    \begin{subfigure}[t]{0.45\textwidth}
        \centering
        \includegraphics[scale=0.17]{R_case1}
        \caption{Tail recycling}
        \label{sfig:case1_R}
    \end{subfigure}
    \caption{Evolution of the product assays at each level with considering
    miss-use model A, with (right) and without recycling (left).}
    \label{fig:case1}
\end{figure}

\begin{figure}[h!]
    \centering
    \begin{subfigure}[t]{0.45\textwidth}
        \centering
        \includegraphics[scale=0.17]{NR_case2}
        \caption{No tail recycling}
        \label{sfig:case2_NR}
    \end{subfigure}%
    \begin{subfigure}[t]{0.45\textwidth}
        \centering
        \includegraphics[scale=0.17]{R_case2}
        \caption{Tail recycling}
        \label{sfig:case2_R}
    \end{subfigure}
    \caption{Evolution of the product assays at each level with considering
    miss-use model B, with (right) and without recycling (left).}
    \label{fig:case2}
\end{figure}

@@

As shown on Figures \ref{sfig:case1_R}, \ref{sfig:case2_R} and
\ref{sfig:case3_R}, recycling the tails increases the overall product assay at
all the different levels. As the tail assay of a level $n$ is always higher than
the product assay of the level $n-2$, recycling the tails of level $n$ will
consequently increase the feed assay of level $n-1$ (see Table \ref{tab:level}).
Moreover, with an increased feed assay, tail and product assays increase as
well, increasing de facto the feed assays of respectively cascade levels $n-2$
and $n$...  This effect reduces the number of cascade levels required to reach
\gls{HEU} in case A and C.

\begin{figure}[h!]
    \centering
    \begin{subfigure}[t]{0.45\textwidth}
        \centering
        \includegraphics[scale=0.17]{NR_case3}
        \caption{No tail recycling}
        \label{sfig:case3_NR}
    \end{subfigure}%
    \begin{subfigure}[t]{0.45\textwidth}
        \centering
        \includegraphics[scale=0.17]{R_case3}
        \caption{Tail recycling}
        \label{sfig:case3_R}
    \end{subfigure}
    \caption{Evolution of the product assays at each level with considering
    miss-use model C, with (right) and without recycling (left).}
    \label{fig:case3}
\end{figure}

@@

\begin{figure}[h!] % replace 't' with 'b' to force it to be on the bottom
    \centering
    \includegraphics[scale=0.25]{HEU_prod_rate}
    \caption{Production rate for the different model configuration, with in blue
    the case without tail recycling, in orange with tail recycling, and in green
    the reference one. Where A-B-C represent the model used, and NR-R
    respectively the case without tail recycling and the case with tail recycling}
    \label{fig:HEU_rate}
\end{figure}

>>>>

Model       &        &           & A/NR      & A/R       & B/NR      & B/R      & C/NR       & C/R          \\
%Recycling   &        &           & No        & yes       & No        & Yes     & No        & yes        \\
\midrule                                                                                                 
        &            & Feed      & $0.71w\%$ & $1.3w\%$  & $0.71w\%$ & $0.94w\%$ & $0.71w\%$ & $1.66w\%$ \\
Level 0 & Assay      & Product   & $4.13w\%$ & $7.7w\%$  & $4.13w\%$ & $5.43w\%$ & $4.13w\%$ & $9.53w\%$ \\
        &            & Tails      & $0.29w\%$ & $0.5w\%$  & $0.29w\%$ & $0.39w\%$ & $0.29w\%$ & $0.69w\%$  \\
        & Cascades   &           & 26.73     & 26.45     & 26.6      & 25.8      & 26.73     & 26.45      \\
\midrule                                                                                                 
        &            & Feed      & $4.13w\%$ & $11.9w\%$ & $4.13w\%$ & $6.84w\%$ & $4.13w\%$ & $13.0w\%$ \\
Level 1 & Assay      & Product   & $22.8w\%$ & $55.7w\%$ & $20.6w\%$ & $30.7w\%$ & $22.9w\%$ & $69.8w\%$ \\
        &            & Tails      & $1.8w\%$  & $6.6w\%$  & $1.72w\%$ & $2.91w\%$ & $1.81w\%$ & $9.43w\%$  \\
        & Cascades   &           & 2.92       & 3.20      & 2.91      & 3.41     & 2.92      & 3.20       \\
\midrule                                                                                                 
        &            & Feed      & $22.8w\%$ & $55.7w\%$ & $20.6w\%$ & $34.3w\%$ & $22.9w\%$ & $72.6w\%$ \\
Level 2 & Assay      & Product   & $78.5w\%$ & $95.0w\%$ & $61.0w\%$ & $75.8w\%$ & $82.0w\%$ & $98.4w\%$ \\
        &            & Tails      & $4.12w\%$ & $50.9w\%$ & $9.56w\%$ & $17.5w\%$ & $15.7w\%$ & $69.4w\%$ \\
        & Cascades   &           & 0.31      & 0.35      & 0.37      & 0.64      & 0.32      & 0.35      \\
\midrule                                                                                                 
        &            & Feed      & $78.5w\%$ & N.A.      & $61.0w\%$ & $75.8w\%$ & $82.3w\%$ & N.A.      \\
Level 3 & Assay      & Product   & $98.2w\%$ & N.A.      & $90.4w\%$ & $95.0w\%$ & $99.1w\%$ & N.A.      \\
        &            & Tails      & $76.1w\%$ & N.A.      & $79.3w\%$ & $56.1w\%$ & $80.3w\%$ & N.A.      \\
        & Cascades   &           & 0.03      & N.A.      & 0.080     & 0.18      & 0.03      & N.A.      \\
\bottomrule
\end{tabular}
  \label{tab:level}
\end{table}

@@

\begin{figure}[h!]
    \centering
    \begin{subfigure}[t]{0.45\textwidth}
        \centering
        \includegraphics[scale=0.17]{NR_case1}
        \caption{No tails recycling}
        \label{sfig:case1_NR}
    \end{subfigure}%
    \begin{subfigure}[t]{0.45\textwidth}
        \centering
        \includegraphics[scale=0.17]{R_case1}
        \caption{Tails recycling}
        \label{sfig:case1_R}
    \end{subfigure}
    \caption{Evolution of the product assays at each level with considering
    misuse model A, with (right) and without recycling (left).}
    \label{fig:case1}
\end{figure}

\begin{figure}[h!]
    \centering
    \begin{subfigure}[t]{0.45\textwidth}
        \centering
        \includegraphics[scale=0.17]{NR_case2}
        \caption{No tails recycling}
        \label{sfig:case2_NR}
    \end{subfigure}%
    \begin{subfigure}[t]{0.45\textwidth}
        \centering
        \includegraphics[scale=0.17]{R_case2}
        \caption{Tails recycling}
        \label{sfig:case2_R}
    \end{subfigure}
    \caption{Evolution of the product assays at each level with considering
    misuse model B, with (right) and without recycling (left).}
    \label{fig:case2}
\end{figure}

@@

As shown on Figures \ref{sfig:case1_R}, \ref{sfig:case2_R} and
\ref{sfig:case3_R}, recycling the tails increases the overall product assay at
all the different levels. As the tails assay of a level $n$ is always higher than
the product assay of the level $n-2$, recycling the tails of level $n$ will
consequently increase the feed assay of level $n-1$ (see Table \ref{tab:level}).
Moreover, with an increased feed assay, tails and product assays increase as
well, increasing de facto the feed assays of respectively cascade levels $n-2$
and $n$...  This effect reduces the number of cascade levels required to reach
\gls{HEU} in case A and C.

\begin{figure}[h!]
    \centering
    \begin{subfigure}[t]{0.45\textwidth}
        \centering
        \includegraphics[scale=0.17]{NR_case3}
        \caption{No tails recycling}
        \label{sfig:case3_NR}
    \end{subfigure}%
    \begin{subfigure}[t]{0.45\textwidth}
        \centering
        \includegraphics[scale=0.17]{R_case3}
        \caption{Tails recycling}
        \label{sfig:case3_R}
    \end{subfigure}
    \caption{Evolution of the product assays at each level with considering
    misuse model C, with (right) and without recycling (left).}
    \label{fig:case3}
\end{figure}

@@

\begin{figure}[h!] % replace 't' with 'b' to force it to be on the bottom
    \centering
    \includegraphics[scale=0.25]{HEU_prod_rate}
    \caption{Production rate for the different model configuration, with in blue
    the case without tails recycling, in orange with tails recycling, and in green
    the reference one. Where A-B-C represent the model used, and NR-R
    respectively the case without tails recycling and the case with tails recycling}
    \label{fig:HEU_rate}
\end{figure}
